FraCaS: 80 percent complete

### 2019-02-26 paper2018/paper.tex
fix cite

For this reason, and despite the dominance of DL approaches in pretty
much all NLP tasks, logical approaches continue to be
developed and evaluated on datasets like the FraCaS test suite and the
SICK dataset \cite{marelli:2014}.  \citet{bernardy:2017} define a
correspondence between abstract syntax parse trees of the FraCas
examples, parsed using the Grammatical Framework (GF,
\citet{Ranta:GF}), and modern type-theoretic semantics that are output
in the Coq proof assistant (the FraCoq system).  The accuracy is 0.85
for 5 sections of the FraCaS test suite. The \textsc{Langpro} system
presented by \citet{abzianidze:2015} is based on a Natural Logic
tableau theorem prover. It achieves an accuracy of .82 on the SICK
dataset.

@@

\providecommand\forcecenter{\multicolumn{1}{c}}
\providecommand\ncases[1]{{\ensuremath{^{#1}}}}
\begin{table}
  \centering
  \small
\begin{tabularx}{\columnwidth}{Xr@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r}
Section      & {\kern -2em} \#cases & Ours     & FC & MINE & Nut  & Langpro  \\ \hline
Quantifiers  & 75          & .96  & .96    & .77  & .53  & .93  \\
             &             & \ncases{74}     &        &      &      &     \ncases{44} \\
Plurals      & 33          & .82      & .76    & .67  & .52  & .73 \\
      &          &       &     &   &   & \ncases{24} \\
Anaphora     & 28          & .86      &   -    & -    & -    &  -       \\
Ellipsis     & 52          & .87      &   -    & -    & -    &  -       \\
Adjectives   & 22          & .95 & .95    & .68  & .32  & .73 \\
             &          &  \ncases{20} &     &   &   &  \ncases{12} \\
Comparatives {\kern -1em}& 31          & .87      & .56    & .48  & .45  &  -       \\
Temporal     & 75          &  -       &   -    &   -  &  -   &  -       \\
Verbs        & 8           & .75      &   -    & -    & -    &  -       \\
Attitudes    & 13          & .92      & .85    & .77  & .46  & .92  \\ 
    &          &       &     &   &   & \ncases {9}  \\ \hline
Total        & 337         & .89      & .83    & .69  & .50  & .85  \\
             &             & \ncases{259}    & \ncases{174}  & \ncases{174}& \ncases{174}& \ncases{89}
  \end{tabularx}
  \caption{Overview of the accuracy of our system compared to others.
    ``Ours" refers to the approach presented in this paper. When a
    system does not handle the nominal number of test cases (shown in
    the third column), the actual number of test cases attempted is
    shown below the accuracy figure, in smaller font.  ``FraCoq''
    refers to the work of \citet{bernardy_type_2017}. ``MINE" refers
    to the approach of \citet{Mineshima:2015}, ``NUT" to the CCG
    system that utilizes the first-order automated theorem prover
    \textit{nutcracker} described by \citet{bos:2008}, and ``Langpro"
    to the system presented by \citet{abzianidze:2015}. A dash
    indicates that no attempt was made for a given section. }
  \label{tab:results}
\end{table}

>>>>

For this reason, and despite the dominance of DL approaches in pretty
much all NLP tasks, logical approaches continue to be
developed and evaluated on datasets like the FraCaS test suite and the
SICK dataset \cite{marelli:2014}.  \citet{bernardy:2017} define a
correspondence between abstract syntax parse trees of the FraCas
examples, parsed using the Grammatical Framework (GF,
\citet{Ranta:GF}), and modern type-theoretic semantics that are output
in the Coq proof assistant (the FraCoq system).  The accuracy is 0.85
for 5 sections of the FraCaS test suite. The \textsc{Langpro} system
presented by \citet{Abzianidze:2015} is based on a Natural Logic
tableau theorem prover. It achieves an accuracy of .82 on the SICK
dataset.

@@

\providecommand\forcecenter{\multicolumn{1}{c}}
\providecommand\ncases[1]{{\ensuremath{^{#1}}}}
\begin{table}
  \centering
  \small
\begin{tabularx}{\columnwidth}{Xr@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r}
Section      & {\kern -2em} \#cases & Ours     & FC & MINE & Nut  & Langpro  \\ \hline
Quantifiers  & 75          & .96  & .96    & .77  & .53  & .93  \\
             &             & \ncases{74}     &        &      &      &     \ncases{44} \\
Plurals      & 33          & .82      & .76    & .67  & .52  & .73 \\
      &          &       &     &   &   & \ncases{24} \\
Anaphora     & 28          & .86      &   -    & -    & -    &  -       \\
Ellipsis     & 52          & .87      &   -    & -    & -    &  -       \\
Adjectives   & 22          & .95 & .95    & .68  & .32  & .73 \\
             &          &  \ncases{20} &     &   &   &  \ncases{12} \\
Comparatives {\kern -1em}& 31          & .87      & .56    & .48  & .45  &  -       \\
Temporal     & 75          &  -       &   -    &   -  &  -   &  -       \\
Verbs        & 8           & .75      &   -    & -    & -    &  -       \\
Attitudes    & 13          & .92      & .85    & .77  & .46  & .92  \\ 
    &          &       &     &   &   & \ncases {9}  \\ \hline
Total        & 337         & .89      & .83    & .69  & .50  & .85  \\
             &             & \ncases{259}    & \ncases{174}  & \ncases{174}& \ncases{174}& \ncases{89}
  \end{tabularx}
  \caption{Overview of the accuracy of our system compared to others.
    ``Ours" refers to the approach presented in this paper. When a
    system does not handle the nominal number of test cases (shown in
    the third column), the actual number of test cases attempted is
    shown below the accuracy figure, in smaller font.  ``FraCoq''
    refers to the work of \citet{bernardy_type_2017}. ``MINE" refers
    to the approach of \citet{Mineshima:2015}, ``NUT" to the CCG
    system that utilizes the first-order automated theorem prover
    \textit{nutcracker} described by \citet{bos:2008}, and ``Langpro"
    to the system presented by \citet{Abzianidze:2015}. A dash
    indicates that no attempt was made for a given section. }
  \label{tab:results}
\end{table}
